Verifying Demonstrations

### 2020-03-12 paper/DB-Schnorr-nbit.tex
Updates nbit MF proof
This takes the distribution of the bits into consideration.

\begin{proof}
  It follows from the \ac{ZK} property (\cref{UWB-ZKPK}) that the adversary 
  cannot learn anything by observation.
  This leaves the adversary with two options:
  \begin{enumerate}
  \item guess which challenge the verifier will use and request the correct 
    response from the prover, receiving the challenge first would taint the 
    session (\cref{TaintedMF});
  \item guess the response.
  \end{enumerate}

  The first option yields success with probability \(\frac{1}{2}\), since the 
  choice is uniformly distributed over the two challenges.

  The second option yields a lower success probability:
  Assume that each bit reveals some information about the future bits.
  The first bit must still be guessed, this is yields a probability of \emph{at 
  most} \(\frac{1}{2}\).

  The best strategy is to guess which challenge the verifier will select.
  Thus, the success probability is \(\frac{1}{2}\) per round, or 
  \(\frac{1}{2^n}\) in total.
\end{proof}

>>>>

\begin{proof}
  It follows from the \ac{ZK} property (\cref{UWB-ZKPK}) that the adversary 
  cannot learn anything by observation.
  This leaves the adversary with the following:
  \begin{enumerate}
    \item guess which challenge the verifier will use and request the correct 
      response from the prover, receiving the challenge first would taint the 
      session (\cref{TaintedMF});
    \item guess the second response.
  \end{enumerate}

  The first case yields success with probability \(\frac{1}{2}\), since the 
  choice is uniformly distributed over the two challenges.
  The adversary requests all \(|q|\) bits of the response~\(s_{\hat b}\) and 
  \(l\) bits of \(s_{1-\hat b}\).
  When the verifier sends challenge bit \(b_i = \hat b\), the adversary replies 
  with a bit from \(s_{\hat b}\).
  If \(b_i = 1-\hat b\), then the adversary uses the \(l\) bits.

  If the adversary guessed \(\hat b = b\) correctly, then the verifier will 
  accept.
  Otherwise, the adversary must compute the remaining \(|q|-l\) bits of 
  \(s_{1-\hat b}\).

  Guessing the remaining bits yield a success probability of 
  \(\frac{1}{2^{|q|-l}}\).
  \Cref{DBSPtoDLP} states that any algorithm that can compute the remaining 
  bits can also solve a corresponding \ac{DLP}.
  It follows that the adversary cannot do non-negligibly better than guessing 
  the remaining bits.

  Thus, the success probability is \(\frac{1}{2}+\frac{1}{2^{|q|-l}}\) per 
  round, or \(\left(\frac{1}{2}+\frac{1}{2^{|q|-l}}\right)^n\) in total.

\end{proof}
